Leadership across cultures and contexts: an exploratory analysis

### 2020-05-15 leadership_across_cultures_contexts.Rmd
Minor revisions. Pulling.

Research on leadership within anthropology extends to the birth of the discipline. Early on, anthropologists (and some sociologists) realized that leadership and followership were critical to understanding human psychology, social organization, and culture [e.g., @mumford_origins_1906; @firth1927economic; @morgan_ancient_1877; @myres_influence_1917]. Anthropologists have documented the emergence of leaders among every ethnographically observed society [@brown_human_1991; @lewis_leaders_1974], and across diverse social contexts, such as families and kin groups [@dussart2000politics], ritual [@singh_cultural_2017], work groups [@macfarlan_competitive_2012], conflicts between groups [@glowacki_evolutionary_2017], and in nonindustrial political groups [@cohen_comparative_1967]. For review, see @garfield_review_2019.

Leaders substantially shape group structures and outcomes across cultures. The structure of groups and their goals, in turn, as well as their subsistence strategies, can favor particular leader qualities. Despite decades of research and theorizing on leadership in numerous social science disciplines, to our knowledge there is no comprehensive or systematic investigation of leader functions and qualities, and the costs and benefits of leadership and followership, across a representative sample of nonindustrial societies. Moreover, outside of anthropology, most research and theorizing on leadership is based on data from Western or Westernized, postindustrial societies [@von_rueden_leadership_2015].

>>>>

Research on leadership within anthropology extends to the birth of the discipline. Early on, anthropologists (and some sociologists) realized that leadership and followership were critical to understanding human psychology, social organization, and culture [e.g., @mumford_origins_1906; @firth1927economic; @morgan_ancient_1877; @myres_influence_1917]. Anthropologists have documented the emergence of leaders among every ethnographically observed society [@brown_human_1991; @lewis_leaders_1974], and in diverse contexts, such as kin groups [@dussart2000politics], ritual [@singh_cultural_2017], work groups [@macfarlan_competitive_2012], conflicts between groups [@glowacki_evolutionary_2017], and in nonindustrial political groups [@cohen_comparative_1967]. For review, see @garfield_review_2019.

Leaders substantially shape group structures and outcomes. The structure of groups and their goals, in turn, as well as their subsistence strategies, can favor particular leader qualities. Despite decades of research and theorizing on leadership in numerous social science disciplines, to our knowledge there is no comprehensive or systematic investigation of leader functions and qualities, and the costs and benefits of leadership and followership, across a representative sample of nonindustrial societies. Moreover, outside of anthropology, most research and theorizing on leadership is based on data from Western or Westernized, postindustrial societies [@von_rueden_leadership_2015].
